---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# radna

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/radna)](https://CRAN.R-project.org/package=radna)
<!-- badges: end -->

> [!WARNING]  
> This package is in early development and not yet ready for use

radna detects the burden of ionizing radiation-induced mutations from cancer whole-genome data. It has 3 goals

1. Quantify the burden of radiation-induced mutations in the tumour
2. Classify samples as radiation-induced / non-radiation induced
3. Quantify per-mutation probabilities of originating from ionizing radiation damage


## Installation

You can install the development version of radna from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/radna")
```

## Quick Start

This is a basic example which shows you how to solve a common problem:

```{r example}
library(radna)
## basic example code
```

